\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Literatura}

\bibitem[Antecký, 2011]{ant11} Antecký, T., 2011. Vliv modelu pro koeficient odporu na CFD simulaci suspendace v~mechanicky míchané nádobě. \textit{studentská vědecká konference}, ÚCHI VŠCHT, Praha 

\bibitem[ANSYS CFX, 2010]{cfx10} ANSYS Inc., 2010. ANSYS CFX-Solver Theory Guide. \textbf{13}, Canonsburg, Pennsylvania

\bibitem[ANSYS Fluent 12.0, 2009]{flu09} ANSYS Inc., 2009. ANSYS FLUENT 12.0 Theory Guide. Canonsburg, Pennsylvania

\bibitem[Armenante \textit{a kol.}, 1998]{arm98} Armenante, P. M., Nagamine, E. U., Susanto, J., 1998. Determination of correlations to predict the minimum agitation speed for complete solid suspension in agitated vessels. \textit{The Canadian Journal of Chemical Engineering}, \textbf{76}, 413--419

\bibitem[Baldi \textit{a kol.}, 1978]{bal78} Baldi, G., Conti, R., Alaria, E., 1978. Complete suspension of particles in mechanically agitated vessels. \textit{Chemical Engineering Science}, \textbf{33}, 21--25 

\bibitem[Bittorf a Kresta, 2002]{bit02} Bittorf, K. J., Kresta, S. M., 2002. Prediction of cloud height for solid suspension in stirred tanks. \textit{CHISA Conference Proc.}, Prague

\bibitem[Bohnet a Niesmak, 1980]{boh80} Bohnet, M., Niesmak, G., 1980. Distribution of solids in stirred suspensions. \textit{German
Chemical Engineering}, \textbf{3}, 57--65

\bibitem[Brucato \textit{a kol.}, 1998]{bru98} Brucato, A., Grisafi, F., Montante, G., 1998. Particle drag coefficients in turbulent fluids. \textit{Chemical Engineering Science}, \textbf{43}, 3, 3295--3314

\bibitem[Bujalski \textit{a kol.}, 1999]{buj99} Bujalski, W., Takenaka, K., Polini, S., Jahoda, M., Paglianti, A., Takahashi, K., Nienow, A. W., Etchells, A. W., 1999. Suspension and liquid homogenisation in high solids concentration stirred chemical reactors. \textit{Trans. IChemE}, \textbf{77(A)}, 241--247

\bibitem[Choudhury, 1997]{chou97} Choudhury, N. H., 1997. Improved predictive methods for solids suspension in agitated vessels at high solids loadings. \textit{disertační práce},  University of Arkansas, Arkansas

\bibitem[Clift \textit{a kol.}, 1978]{cli78} Clift, R., Grace, J. R., Weber, M. E.,  1978.  Bubbles, drops, and particles. \textit{Academic Press}, New York

\bibitem[Derksen, 2003]{derk03} Derksen, J. J., 2003. Numerical Simulation of solid suspension in a stirred tank. \textit{AIChE Journal}, \textbf{49}, 11, 2700--2714

\bibitem[Gidaspowem \textit{a kol.}, 1992]{gid92} Gidaspow D., Bezburuah, R., Ding, J., 1992. Hydrodynamics of Circulating Fluidized Beds, Kinetic Theory Approach. \textit{Proceedings of the $7^{th}$ Engineering Foundation Conference on Fluidization}, 75--82

\bibitem[Gidaspow, 1994]{gid94} Gidaspow, D., 1994. Multiphase flow and fluidization: Continuum and kinematic theory description. \textit{Academic Press}, New York

\bibitem[Hicks \textit{a kol.}, 1997]{hic97} Hicks M. T., Myers, K. J.,  Bakker, A., 1997. Study of Solid-Liquid Cloud height in solids suspension agitation. \textit{Chemical Engineering Communications}, \textbf{160}, 137--155

\bibitem[Hosseini \textit{a kol.}, 2010]{hos10} Hosseini, S., Dineshkumar, P., Ein-Mozaffari, F., Mehrvar, M., 2010. Study of Solid-Liquid Mixing in Agitated Tanks through Computational Fluid Dynamics Modeling. \textit{Industrial \& Engineering Chemistry Research}, \textbf{49}, 4426--4435

\bibitem[Ihme \textit{a kol.}, 1972]{ihme72} Ihme, F., Schmidt-Traub H., Brauer, H., 1972. Theoretische untersuchung \"uber die Umstr\"omung und den Stoff\"ubergang an Kugeln. \textit{Chemie Ingenieur Technik}, \textbf{44}, 306

\bibitem[Ishii a Zuber, 1979]{ish79} Ishii, M., Zuber, N., 1979, Drag coefficient and relative velocity in bubbly, droplet or particulate flows. \textit{AIChE Journal}, \textbf{28}, 843--855 

\bibitem[Kasat \textit{a kol.}, 2008]{kas08} Kasat, G. R., Khopkar, A. R., Ranade, V. V., Pandit, A. B., 2008. CFD Simulation of Liquid-Phase Mixing in Solid-Liquid Stirred Reactor. \textit{Chemical Engineering Science}, \textbf{63}, 3877--3885

\bibitem[Khopkar \textit{a kol.}, 2006]{kho06} Khopkar, A. R., Kasat, G. R., Pandit, A. B., Ranade, V. V., 2006. Computational Fluid Dynamics Simulation of Solid Suspension in Stirred Slurry Seactor. \textit{Industrial \& Engineering Chemistry Research} \textbf{45}, 4416--4428.

\bibitem[Kresta a Wood, 1991]{kre91} Kresta, S. M., Wood, P. E., 1991. Prediction of three-dimensional turbulent flow in stirred tanks. \textit{AIChE Journal}, \textbf{37}, 448--460 

\bibitem[Ljungqvist a Rasmuson, 2001]{lju01} Ljungqvist, M., Rasmuson, A., 2001. Numerical simulation of the two-phase flow in an axially stirred reactor. \textit{Trans. IChemE}, \textbf{79}, Part A, 533--546

\bibitem[Lun \textit{a kol.}, 1984]{lun84} Lun, C. K. K., Savage, S. B., Jeffrey, D. J., Chepurniy, N., 1984. Kinetic Theories for Granular Flow: Inelastic Particles in Couette Flow and Slightly Inelastic Particles in a General Flow Field. \textit{Journal of Fluid Mechanics}, \textbf{140}, 223--256 

\bibitem[Micale \textit{a kol.}, 2003]{mic04} Micale, G., Grisafi, F., Rizzuti, L., Brucato, A., 2004. CFD simulation of particle suspension height in stirred vessels. \textit{Chemical Engineering Research and Design}, \textbf{82}, 1204--1213

\bibitem[Micheletti \textit{a kol.}, 2003]{miche03} Micheletti, L., Nikiforaki, L., Lee, K. C., Yianeeskis, M., 2003. Integral and Local Concentration Characteristics of Moderate to Dense Solid-Liquid Suspensions. \textit{11$^{th}$ European Conference on Mixing}, Bamberg, Germany

\bibitem[Montante a Bakker, 2004]{mon04} Montante, G., Bakker, A., 2004, Solid-Liquid Multiphase Flow Validation in Tall Stirred Vessels with Multiple Impeller Systems \textit{Technical Notes}, \textbf{TN253}, Fluent Inc.

\bibitem[Nienow, 1968]{nie68} Nienow, A. W., 1968. Suspension of solid particles in turbine agitated baffled vessels. \textit{Chemical Engineering Science}, \textbf{23}, 1453--1459 

\bibitem[Ochieng a Onyango, 2008]{ochi08} Ochieng, A., Onyango, M. S., 2008. Drag models, solids concentration and velocity distribution in a stirred tank. \textit{Powder Technology}, \textbf{181}, 1--8

\bibitem[Oshinowo a Bakker, 2002]{oshi02} Oshinowo, L. M., Bakker, A., 2002. CFD modeling of solids suspensions in stirred tanks. \textit{Symposium on Computational Modeling of Metals, Minerals and Materials}, February 17-21, Seattle, Washington 

\bibitem[Paul \textit{a kol.}, 2004]{paul04} Paul, E. L., Atiemo-Obeng, V. A., Kresta, S. M., 2004. Handbook of Industrial Mixing: Science and Practice. \textit{Wiley-Interscience}, New York

\bibitem[Pavlíková, 2011]{pav11} Pavlíková, Z., 2011. Experimentální studium homogenizace kapalin v přítomnosti pevné zrnité fáze. \textit{bakalářská práce}, ÚCHI VŠCHT, Praha 

\bibitem[Pinelli \textit{a kol.}, 2001]{pin01} Pinelli, D., Nocentini, M., Magelli, F., 2001. Solids distribution in stirred slurry reactors: in influence of some mixer configurations and limits to the applicability of a simple model for predictions.
\textit{Chemical Engineering Communications}, \textbf{188}, 91--107

\bibitem[Sardeshpande \textit{a kol.}, 2010]{sar10} Sardeshpande, M. V., Juvekar, V. A., Ranade, V. V., 2010. Hysteresis in Cloud Heights During Solid Suspension in Stirred Tank Reactor: Experiments and CFD Simulations. \textit{AIChE Journal}, \textbf{56}, 11, 2795---2804

\bibitem[Schiller a Naumann, 1935]{schi32} Schiller, L., Naumann, Z., 1935. A drag coefficient correlation. \textit{Z. Ver. Deutsch. Ing.}, \textbf{77}, 318--320

\bibitem[Syamlalem a O'Brienem, 1993]{syam93} Syamlal, M., O'Brien, T. J., 1993. MFIX Documentation: Theory Guide. \textit{National Technical Information Service}, \textbf{1}, Springfield, Virginia 

\bibitem[Tamburini \textit{a kol.}, 2009]{tamb09} Tamburini, A., Cipollina, A., Micale, G., Ciofalo, M., Brucato, A., 2009. Dense solid–liquid off-bottom suspension dynamics: Simulation and experiment. \textit{Chemical Engineering Research and Design}, \textbf{87}, 587--597

\bibitem[Yamazaki \textit{a kol.}, 2008]{yama08} Yamazaki, H., Tojo, K., Miyanami, K., 1986. Concentration profiles of solids suspended in a stirred tank. \textit{Powder Technology}, \textbf{48}, 205--216

\bibitem[Zwietering, 1957]{zwi58} Zwietering, T. N., 1958. Suspending of solid particles in liquid by agitators. \textit{Chemical Engineering Science}, \textbf{8}, 244--253 

\end{thebibliography}
